%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Director, Developer Productivity} % Job title
    {MatrixCare} % Organization
    {Bloomington, MN} % Location
    {May 2021 - Present (remote)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Manager of all MatrixCare devops/platform ops teams, supporting organizational improvements and initiatives, and driving the teams towards a center of excellence model.}
        \item {Spearheaded modernization and process improvement initiatives, including supporting teams through the process of monolithic decomposition, proper data modeling, microservice development, and rapid product delivery (CI/CD).}
        \item {Member of a cross organizational executive team dedicated to defining operating, architectural and development standards across all Resmed SaaS companies.}
      \end{cvitems}
    }
    
%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Principal Software Engineer - Home Health Division} % Job title
    {MatrixCare} % Organization
    {Bloomington, MN} % Location
    {Oct 2019 - April 2021 (remote)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of the enterprise architecture team, responsible for directing initiatives targeting software quality, proper architectural standards and improvements to devops.}
        \item {Technical oversight for offshore teams.}
        \item {Serving as acting manager of the platform operations team, responsible for driving platform modernization initiatives.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Senior Software Engineer - Homecare Division} % Job title
    {MatrixCare} % Organization
    {Coral Springs, FL} % Location
    {Feb 2008 - Oct 2019 (remote)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Team lead responsible for native mobile application development and deployment. (MatrixCare for Home Care, available on Google Play and Apple's App Store).}
        \item {Developed an electronic visit verification system used by health aides and companions performing in-home tasks. (ASP.NET MVC, AngularJS, Typescript, SQL Server).}
        \item {Developed a clinical point of care web application used by in-home nurses. (ASP.NET MVC, AngularJS, Typescript, SQL Server).}
        \item {Implementing policies for software quality standards including unit and integration test requirements, code reviews, etc..}
        \item {Building and maintaining the continuous integration and deployment pipeline for the homecare division.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Senior Programmer} % Job title
    {White Oak Systems} % Organization
    {Wallingford, CT} % Location
    {Mar 1999 - Feb 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Technical lead for a group of developers working on an enterprise software application for the home health care industry.}
        \item {Managed all aspects of the software development life cycle, including requirements gathering, design, writing specifications, providing reliable time estimates, coding and code reviews, QA, documentation, packaging and deployment.}
         \item {Developed processes for bug tracking, source code management, and developed custom software deployment tools.}
         \item {Implemented coding standards and software development policies.}
         \item {Gained a vast amount of experience in clinical and billing processes, including OASIS and EDI standards.}
      \end{cvitems}
    }

\cventry
    {Programmer} % Job title
    {Pratt \& Whitney} % Organization
    {East Hartford, CT} % Location
    {Mar 1997 - Jan 1999} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Hired into a 2-year rotation program.}
        \item {Materials engineering lab: Creep analysis using LabVIEW, C++ and Fortran.}
         \item {International Aero Engines: Developed databases used for engine part tracking.}
         \item {CAD Group: Engine visualization software (PWLook), and their distributed document management system (DDM) (C++).}
         \item {Fuels and Lubes group: Fluid flow analysis on the F-35 engine mid gearbox using EZ-Flow and C++.}
      \end{cvitems}
    }
    

\end{cventries}
